Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-05 ms.tex
more

Following \citet{Quataert:2004a} (see also \citealt{HolzerAxford:1970a,De-ColleGuillochon+:2012a,ShcherbakovWong+:2014a}), we calculate the density $\rho$, temperature $T$, and radial velocity $v$ of the CNM for each galaxy model by solving the equations of one-dimensional, time-dependent hydrodynamics,
\begin{align}
  &\drhodt+\frac{1}{r^2}\frac{\partial}{\partial r}\left(\rho r^2 v\right)=q \label{eq:drhodt}\\
  &\rho \left(\frac{\partial v}{\partial t} + v\frac{\partial
      v}{\partial r}\right) =-\frac{\partial p}{\partial r}- \rho\frac{GM_{\rm enc}}{r^{2}} -q v \label{eq:dvdt}\\
  &\rho T\left(\frac{\partial s}{\partial t} + v\frac{\partial
      s}{\partial r}\right)=q\left[\ke+\kew-\gammaf \cs \right] 
, 
\label{eq:dsdt}
\end{align}
where $p$ and $s$ are the pressure and specific entropy, respectively, and $M_{\rm enc} = M_{\star}(r) + \Mbh$ is the
enclosed mass.  We adopt an ideal gas equation of state with $p = \rho kT/\mu m_p$ with $\mu = 0.62$  and $\gamma = 5/3$.

>>>>

Following \citet{Quataert:2004a} (see also \citealt{HolzerAxford:1970a,De-ColleGuillochon+:2012a,ShcherbakovWong+:2014a}), we calculate the density $\rho$, temperature $T$, and radial velocity $v$ of the CNM for each galaxy model by solving the equations of one-dimensional, time-dependent hydrodynamics,
\begin{align}
  &\drhodt+\frac{1}{r^2}\frac{\partial}{\partial r}\left(\rho r^2 v\right)=q \label{eq:drhodt}\\
  &\rho \left(\frac{\partial v}{\partial t} + v\frac{\partial
      v}{\partial r}\right) =-\frac{\partial p}{\partial r}- \rho\frac{GM_{\rm enc}}{r^{2}} -q v \label{eq:dvdt}\\
  &\rho T\left(\frac{\partial s}{\partial t} + v\frac{\partial
      s}{\partial r}\right)=q\left[\ke+\kew-\gammaf \cs \right] 
, 
\label{eq:dsdt}
\end{align}
where $p$ and $s$ are the pressure and specific entropy, respectively, and $M_{\rm enc} = M_{\star}(r) + \Mbh$ is the
enclosed mass (we neglect dark matter contributions).  We adopt an ideal gas equation of state with $p = \rho kT/\mu m_p$ with $\mu = 0.62$  and $\gamma = 5/3$.
